
The term Command and Control (C2) can be applied in many scenarios, from finances to military operations. It reminds a high level control of the situation, resources and plan execution. Actually, the C2 term has all these relations but in Inforamtion Age, 21th Century, this concept needs to be extended to and evolved to include a wider definition.

Original definition applied to C2 is linked with the classical military strategies applied in XIX and XX centuries, with a central commander and an inflexible hierarchical chain. However, this concept is totally incompatible with the modern warfare and environment.

The DoD defines C2 as the exercise of authority and direction by a properly designated commander over assigned and attached forces in the accomplishment of the mission \cite{States.2019}. However, this and many other definitions does not permit to identify the existence of C2 in the organization and its assessment.

This definition is more compatible when we have a static scenario where changes do not occur. In this case, the entities evolved behaviour are predictable and it is not required to have a mechanism to do a constant monitoring. However, C2 is a concept that naturally evolves a dynamic context because it empowers the system with the capacity to deal with changes in circumstances.

To keep the C2 ability is mandatory to have the capacity to monitor and to share information about the changes that occur in the context. Any kind of modification in the scenario, in the members or even in the mission to be performed is important to be monitored to do not loose the team focus.

Self-adaptive systems are currently widely used to deal with scenarios where there are changes during systems execution. The ability to adapt itself to attend new requirements from the environment or from the user, becomes useful in many circumstances.

The changes of a singular component or a set of components are motivated by context changes. This context is defined by the environment where it is, the tasks or activities to be done and the status of the entities.

According to Stanton et al. \cite{} and  Mason et al. \cite{}, C2 relies on the information and awareness sharing. It is not a simple data spread. The information needs to respect the rules and logical conditions to reach the right target and to cause the right effect. This information sharing occurs on a network structure that satisfies the context requirements, including mission details and context restrictions.

